--- 
title: "Modelos Bayesianos de Población para América Latina y el Caribe Implementación, Validación y Aplicación Subnacional"
author: "Andrés Gutiérrez^[Experto Regional en Estadísticas Sociales - Comisión Económica para América Latina y el Caribe (CEPAL) -  andres.gutierrez@cepal.org],Stalyn Guerrero^[Consultor - Comisión Económica para América Latina y el Caribe (CEPAL), guerrerostalyn@gmail.com]"
date: "`r Sys.Date()`"
lang: es
documentclass: book
# bibliography: [CEPAL.bib]
biblio-style: apalike
link-citations: yes
colorlinks: yes
lot: yes
lof: yes
fontsize: 12pt
geometry: margin = 3cm
header-includes:
  - \usepackage{amsmath}
  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
  - \usepackage{hyperref}
github-repo: psirusteam/2021ASDA
description: "Este es el repositorio del libro *Análisis de encuestas con R*."
knit: "bookdown::render_book"
linkcolor: blue
output:
  pdf_document:
    toc: true
    toc_depth: 3
    keep_tex: true
    latex_engine: xelatex
  gitbook:
    df_print: kable
    css: "style.css"
# Compilar así:
# bookdown::render_book("index.Rmd", "bookdown::pdf_book")
# bookdown::render_book("index.Rmd", "bookdown::epub_book")
# bookdown::render_book("index.Rmd", "bookdown::word_document2")
# bookdown::preview_chapter("01.Rmd", "bookdown::word_document2")
---
# About

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports; for example, a math equation $a^2 + b^2 = c^2$.

## Usage 

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Render book

You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
